Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
writing Sec 5.2 (Doctest).

@@

\begin{itemize}
    \item
        Doctest uses the GHC API to extract Haddock comments.
    \item
        It uses the GHC API directly, so that it can more easily
        support old GHC versions.  Each release of Haddock only
        supports the latest GHC version.
    \item
        Doctest use GHCi to verify examples.
    \item
        It reuses the same GHCi session for all examples.
    \item
        Examples from the same Haddock comment are grouped together,
        and share the same scope.
    \item
        The scope is cleared with \verb|:reload| before a new
        Example group is started.
    \item
\end{itemize}

Since test is done by comparing result string in Haddock notation and
result string from GHCi, exceptions can be handled.

>>>>

To extract evidence from Haddock markup,
Doctest used Haddock API in the past.
Since Each release of Haddock supports only the latest version of GHC,
it is difficult to support old versions of GHC with Haddock API.
Doctest is now directly using GHC API for portability.

@@

To verify examples, Doctest uses GHCi.
Test is done by comparing result string in Haddock notation and
result string from GHCi.
Since verification based on string comparison, exceptions can be handled.

Doctest reuses the same GHCi session for all examples in a module.
Examples from the same Haddock comment are grouped together,
and share the same scope.
The scope is cleared with \verb|:reload| before a new
Example group is started.
